Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-04-25 source/sec_theorems.tex
added result summary

>>>>

Linear speedup of SGD and Nesterov SGD for strongly convex and smooth
objectives: full participation $O(\frac{\nu_{max}^{2}\sigma^{2}}{NT}+\frac{E^{2}LG^{2}}{T^{2}})$
with $\nu_{max}=N\cdot\max_{k}p_{k}$; partial participation $O(\frac{\nu_{max}^{2}\sigma^{2}+4E^{2}G^{2}L}{KT})$.
In particular, this implies full participation allows $E=O(\sqrt{\frac{T}{N}})$
to achieve $O(1/NT)$, whereas partial participation only allows $E=O(1)$
to achieve $O(1/KT)$.

Other accelerations likely not possible.
